Parsing Postfix log files

### 2007-12-18 doc/logparser.tex
Started on the overall conclusion.  I want to get Carl's opinion before taking it much further; I reckon I need to expand it to at least a page, if not two.

\section{Conclusion}

@@

XXX WRITE THIS

>>>>

\newpage
\section{Conclusion}

@@

Parsing Postfix logs appears at first sight to be an almost trivial task,
especially given previous experience in parsing logs, but it turns out to
be a much more taxing project than initially expected.  The variety and
breadth of log lines produced by Postfix is quite surprising, as a quick
survey of sample log files gives the impression that the number of distinct
log lines is quite small; this impression is due to the uneven distribution
evidenced by logs produced in normal operation (see graph~\refwithpage{rule
hits graph} for a vivid illustration of this).

Enabling users to easily extend the parser to deal with new log lines is a
design imperative, and despite the resulting increase in complexity the job
is quite tractable, though it does raise interesting efficiency and
optimisation questions (answered in section~\refwithpage{rule efficiency}).
For the parser to be useful to the average user, parsing new log lines
produced by Postfix must be as simple a task as configuring Postfix to
produce those log lines was in the first place, otherwise users won't make
to effort to utilise the parser.  Providing a tool to ease the generation
of \regexes{} from unparsed log lines should help

The real difficulties arise once the parser is successfully dealing with
90\% of the log lines, as the irregularities and complications previously
explained only begin to become apparent once the vast majority of log lines
have been parsed successfully.  Dealing with numerous, infrequently
occurring log lines is a simple, albeit tiresome task, whereas dealing with
information which hasn't been logged, e.g.\ when delivery attempts are
aborted.
